\documentclass{sig-alternate}
\usepackage{url}

%% Bring items closer together in list environments
% Prevent infinite loops
\let\Itemize =\itemize
\let\Enumerate =\enumerate
\let\Description =\description
% Zero the vertical spacing parameters
\def\Nospacing{\itemsep=0pt\topsep=0pt\partopsep=0pt\parskip=0pt\parsep=0pt}
% Redefine the environments in terms of the original values
\renewenvironment{itemize}{\Itemize\Nospacing}{\endlist}
\renewenvironment{enumerate}{\Enumerate\Nospacing}{\endlist}
\renewenvironment{description}{\Description\Nospacing}{\endlist}

\begin{document}
\conferenceinfo{UWCSE503}{'10 Seattle, WA USA}

\title{JavaGrok: Automatic Inference of Documentation for Under-documented Code}

\numberofauthors{1} 
\author{
\alignauthor
Colin S. Gordon, Reto Conconi, Gilbert Bernstein, Michael Bayne\\
       \affaddr{University of Washington}\\
       \affaddr{Seattle, WA USA}\\
       \email{\{csgordon,conconir,gilbo,mdb\}@cs.washington.edu}
}

\maketitle
\begin{abstract}
Modern software development increasingly involves the use of third party
libraries. Developers now routinely locate and learn the APIs of myriad
libraries in the course of a single software development project. This process
is made more difficult by the fact that many libraries are poorly documented.
The developer often has to read the library source code or resort to trial and
error to determine how to correctly use the library. These methods of learning
about the library are time consuming and error prone.

We present a method to automatically augment library API documentation with invariants
inferred by a variety of static analyses. These include argument nullability,
argument and receiver mutation, argument leaking and capturing, and conditions
that will cause exceptions to be thrown.
\end{abstract}

% These categories are from the ACM CCS (Computing Classification System)
% http://portal.acm.org/ccs.cfm
\category{F.3.1}{Specifying and Verifying and Reasoning about
Programs}{Specification techniques}
\category{D.2.7}{Distribution, Maintenance, and Enhancement}{Documentation}
\category{D.2.13}{Software Engineering}{Reusable Software}

% These "terms" are from the ACM's official General Terms classifications.
% http://www.acm.org/about/class/1998
\terms{Documentation, Human Factors, Languages}

\keywords{Documentation Inference, Software Documentation, Static Analysis}

\input{intro.tex}

\input{approach.tex}

\input{evaluation.tex}

\input{related.tex}

\input{conclusion.tex}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
The authors thank the Great Pumpkin.

\bibliographystyle{abbrv}
\bibliography{javagrok}

\end{document}
